### 2015-01-14 src/introduction.Rnw
update

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
250 Java programs from Github\footnote{Our dataset is 322 programs, but as of
this writing the larger projects have not completed finished running
full-mutation analysis.},
with size ranging from $50$ to $100,000$ lines (excluding tests), allowing
us to draw more widely applicable statistical inferences.

% For a mutation selection strategy to be considered effective, especially during
% the development, it should be able to expose as many defect-like behaviors as
% possible.
Consider any test in a test suite. It is written with the intent of
checking for the absence of some (faulty) behavior. If supposing, tests
were equivalent in the number of behaviors that they test, then the best test
suite would be one that included the largest number of non-redundant test
cases~\footnote{We show later why this assumption is valid (Specifically,
assertion distribution was $\mu=1.7$ and $\sigma=2$ )}. This suggests that
we could evaluate different mutation reduction strategies on their ability
to choose mutants such that they are killed by a larger number of
non-redundant test cases. Further, such a technique is not limited by the
adequacy of test suite under consideration.

Section~\ref{sec:methodology} discusses the sampling and operator
selection strategies we study in detail, and the results of our
experiment are given in Section~\ref{sec:results}, followed by
detailed discussion of what these results imply in Section
~\ref{sec:discussion}. The specific contributions of this paper are:

@@

\item Our study is the largest so far in terms of
both the size of programs involved (50 LOC to 100 KLOC excluding tests),
and the number of programs analyzed (250 unique open source projects) for
mutant reduction strategies. This allows for stronger and more widely
applicable conclusions about effectiveness.

\item We compare a much larger
number of mutant reduction strategies than previous studies. Our reduction
strategies include all the common and influential strategies for
random sampling, element scoped sampling, and operator selection, that
have been proposed in previous studeies.

>>>>

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
312 Java programs from Github, with size ranging from $50$ to $100,000$
lines (excluding tests), allowing us to draw more widely applicable
statistical inferences.

% For a mutation selection strategy to be considered effective, especially during
% the development, it should be able to expose as many defect-like behaviors as
% possible.
Consider any test in a test suite. It is written with the intent of
checking for the absence of some (faulty) behavior. From the perspective of a
a tester, the best testsuite is one that checks for the absence
of the largest number of faulty behaviors. If tests were equivalent in the
amount of behaviors that they verify, then the best testsuite would be one that
encouraged adding the largest number of non-redundant test cases. However,
it is possible that different tests are not equivalent in the number of
behaviors that they check. We can approximate this to some extent by
including the number of assert statements within each test~\footnote{We
approximate the effect of exception-only test cases by starting the assert
count from $1$ rather than $0$}.

Hence an easy way to evaluate a mutation reduction strategy would be to
see if it promotes such test suites; that is, either test suites with a large
number of non-redundant test cases, or those with a large number of asserts.

If we assume that testers would prefer adding test cases that increases the
mutation score, then a good strategy should reward the behavior of adding
non-redundant test cases and test suites with larger number of asserts.
Thus it should choose a set of mutants that are killed by a larger number
of such non-redundant tests at-least in comparison with random selection
of the same number of mutants as the chosen set. We could also ensure that
a reduction strategy does not miss out on important tests by running the
set of non-redundant tests against the full set of mutants to see how many
of the mutants were detected in comparison with the original number of
detected mutants. Since this evaluation crtieria does not depend on the
mutation-adequacy of the test suite under consideration, we can run the
evaluation using real world projects which almost always have non-adequate
test suites.

Section~\ref{sec:related} describes the research in mutation reduction 
strategies. Section~\ref{sec:methodology} discusses the sampling and
operator
selection strategies we study in detail. The analysis is given in
Section~\ref{sec:analysis}, and the results of our
experiment are given in Section~\ref{sec:results}, followed by
detailed discussion of what these results imply in Section
~\ref{sec:discussion}. The specific contributions of this paper are:

@@

\item Our study is the largest so far in terms of
both the size of programs involved ($50$ to $100,000$ lines excluding tests),
and the number of programs analyzed ($312$ unique open source projects) for
mutant reduction strategies. This allows for stronger and more widely
applicable conclusions about effectiveness.

\item We compare a much larger
number of mutant reduction strategies than previous studies. Our reduction
strategies include all the common and influential strategies for
random sampling, element scoped sampling, operator based sampling,
and operator selection, that have been proposed in previous studeies.
